\chapter{Project Description}
\label{ch:description}

Provide details of the solution in the coming sections.

\section{Scope}
Write down the scope of your project in a paragraph. Briefly define the main functionalities of the proposed project. Scope defines the boundaries and range of the proposed solution, that would be the part of your project. Write down in logical flow with consistency. 
(Usually in 14-18 sentences)

\section{Modules}
Write down the modules of the proposed project.   
Each module should highlight features, using bulleted/numbered notation. 
When developing both a mobile app and a web app, group the modules according to the system types, such as, Client Web App, Client Mobile App, Admin Web App etc.

\subsection{Module 1}
[2-4 lines description of the module]
\begin{enumerate}
    \item Feature 1
    \item Feature 2
\end{enumerate}

\subsection{Module 2}
[2-4 lines description of the module]
\begin{enumerate}
    \item Feature 1
    \item Feature 2
\end{enumerate}


\section{Tools and Technologies}
Provide a detail of the tools and technologies required for this project.

\section{Work Division}
For each module and respective feature,  assign responsibility to a team member
\begin{table}[!h]
\caption{Table 1}
\begin{tabular}{|lll|}
\hline
Name   & Registration   & Responsibility/ Module / Feature   \\ \hline
Mr. Ali & 22i-0000 & (Module 1- Feat 1-3) Augmented reality and Database tasks    \\ \hline  
\end{tabular}
\end{table}

\section{TimeLine}
Create a timeline relating each iteration to the tasks/modules created previously.

\begin{table}[!h]
\caption{Table 2}
\begin{tabular}{|lll|} \hline
Iteration\# & Time frame & Tasks/Modules                        \\ \hline
01          & Sept-Oct   & User Authentication, Audio Analysis  \\ \hline
02          & Nov-Dec    & Report generation, Candidates Raking \\ \hline
\end{tabular}
\end{table}